|

### 2024-12-20 Drafts/Paper_1/appendix.Rmd
Christmas Gift
Edits from the summer finally all done. Biggest hang up is the discussion at the moment.

---
output:
  pdf_document:
    fig_caption: yes
    extra_dependencies: float
linkcolor: blue
header-includes: \usepackage{float}
editor_options:
  chunk_output_type: console
---

```{r, include=F, echo=F}
knitr::opts_knit$set(eval.after = "fig.cap")
knitr::opts_chunk$set(fig.pos = 'H')
options(knitr.kable.NA = '')
require(tidyverse)
options(tinytex.verbose = TRUE)

```

# Figures {-}

```{r lambda-bx-6-fig, echo=F, fig.cap="$\\lambda$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"))

```

\newpage
```{r lambda-bx-other-fig, echo=F, fig.cap="$\\lambda$ estimates for the remainded of the stocks in this analysis, plotted by the location of the stock. The abreviated species name is provided on the x axis."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"))

```

\newpage
```{r lambda-sd-fig, echo=F, fig.cap="Standard deviation of the $\\lambda$ estimates for each stock, ordered by species, in this analysis. "}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"))
```

\newpage
```{r dd-overall-plt, echo=F, fig.cap="Density dependence of $\\lambda$ The top panel shows $\\lambda_{F=0}$ against the proportion of maximum abundance, with a GAM smooth and the GAM estimated 95\\% confidence interval. The middle panel shows $\\lambda_{F>0}$ against the proportion of maximum abundance, with a GAM smooth and the GAM estimated 95% confidence interval. The bottom panel compares the GAM smooths for $\\lambda_{F=0}$ and $\\lambda_{F>0}$."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"))
```

\newpage
```{r dd-nf-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F=0}$ for each stock in the analysis plotted regionally."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"))
```

@@

\newpage
```{r r0-6-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"))
```

\newpage
```{r r0-other-plt, echo=F, fig.cap="$R_0$ estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"))
```

@@

\newpage
```{r gl-6-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"))
```

\newpage
```{r gl-other-plt, echo=F, fig.cap="Generation length estimates for each stock of G. morhua, M. aeglefinus, P. virens, C. harengus, P. platessa, and S. solea."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"))
```

@@

<!-- Now for the Doubling time -->

\newpage
```{r dub-time-map, echo=F, fig.cap="Doubling time estimate for each stock with no fishing mortality."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"))
```

@@

\newpage
```{r dub-vs-sd, echo=F, fig.cap="The recovery potential (low, moderate, or high) of each stock after 20 years compared to the median $\\lambda_{F=0}$ and the standard deviation of $\\lambda_{F=0}$."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"))
```

# Supplemental Figures {-}

>>>>

# APPENDIX A {#app:A}

<!-- f -->
\newpage
```{r dd-nf-stock-plt, echo=F, fig.cap="Density dependence of $\\lambda_{F=0}$ for each stock in the analysis plotted regionally."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"))
```

@@

\newpage
```{r r0-other-plt, echo=F, fig.cap="$R_0$ estimates for the remainder of the stocks in this analysis, plotted by the location of the stock. The abbreviated species name is provided on the x axis."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"))
```

@@

\newpage
```{r gl-other-plt, echo=F, fig.cap="Generation length estimates for the remainder of the stocks in this analysis, plotted by the location of the stock. The abbreviated species name is provided on the x axis."}
knitr::include_graphics(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"))
```

@@

@@

### 2024-12-20 Drafts/Paper_1/index.Rmd
Christmas Gift
Edits from the summer finally all done. Biggest hang up is the discussion at the moment.

header: "Draft working paper --- Do not cite or circulate" # or "" to omit
output:
 csasdown::resdoc_word:
   french: false
   copy_sty: true
   line_nums: true
   line_nums_mod: 1
   lot_lof: false
   draft_watermark: false
   include_section_nums: true
   highlight: tango
# ------------
# End of options to set
knit: (function(input, ...) {
       csasdown::render('_bookdown.yml')
      })
link-citations: true
bibliography: Y:/Zotero/MAR_SABHU.bib
# Any extra LaTeX code for the header:
# header-includes:
# - \usepackage{tikz}
---

>>>>

header: "Draft working paper --- Do not cite or circulate" # or "" to omit
output:
 csasdown::resdoc_word:
   french: false
   copy_sty: true
   line_nums: true
   line_nums_mod: 1
   lot_lof: false
   draft_watermark: false
   include_section_nums: true
   highlight: tango
   number_sections: false
# ------------
# End of options to set
knit: (function(input, ...) {
       csasdown::render('_bookdown.yml')
      })
link-citations: true
bibliography: Y:/Zotero/MAR_SABHU.bib
# Any extra LaTeX code for the header:
# header-includes:
# - \usepackage{tikz}
---
